Natural Selection Across Three Generations of Americans

### 2024-03-04 hrs-selection.qmd
Rerun uncached

```{r}
#| label: stat-bootstraps
#| cache: true
#| cache-lazy: false
#| cache-comments: true

@@

```{r}
#| label: stat-bootstrap-gen-cor
#| cache: true
#| cache-comments: true

@@

```{r}
#| label: stat-bootstrap-gen-cor-gkids
#| cache: true
#| cache-comments: true

@@

```{r}
#| label: stat-x-bootstrap-effect-size
#| cache: true
#| cache-lazy: false
#| cache-comments: true

@@

Why does the US data show fewer differences by socio-economic status (SES) than the UK? One possibility is that in the US, SES maps on to race, so that ethnic differences capture some of the variation seen in the UK. The regression coefficient of phenotypic educational attainment on RLRS is more negative among black than white respondents [blacks: `r tidy_fert_edu_phen$black$estimate`, 95% C.I. `r tidy_fert_edu_phen$black$conf.low` to `r tidy_fert_edu_phen$black$conf.high`, whites: `r tidy_fert_edu_phen$white$estimate`, 95% C.I. `r tidy_fert_edu_phen$white$conf.low` to `r tidy_fert_edu_phen$white$conf.high`; cf. @goldscheider1969minority; @johnson1979minority; @yang2003big; @maralani2013demography]. And the slope of PGS education coefficients on fertility coefficients is larger among black respondents, though imprecisely estimated. But comparisons of PGS selection coefficients between the ethnic groups are hard because of the smaller sample size and differences in the scores' predictive power, so this hypothesis can only be speculative. Another possibility is that the US cohort was exposed to a smaller welfare state than the UK cohort, since many of them had children before the "Great Society" programs of the 1960s.

>>>>

```{r}
#| label: stat-bootstraps
#| cache: false
#| cache-lazy: false
#| cache-comments: true

@@

```{r}
#| label: stat-bootstrap-gen-cor
#| cache: false
#| cache-comments: true

@@

```{r}
#| label: stat-bootstrap-gen-cor-gkids
#| cache: false
#| cache-comments: true

@@

```{r}
#| label: stat-x-bootstrap-effect-size
#| cache: false
#| cache-lazy: false
#| cache-comments: true

@@

Why does the US data show fewer differences by socio-economic status (SES) than the UK? One possibility is that in the US, SES maps on to race, so that ethnic differences capture some of the variation seen in the UK. The regression coefficient of phenotypic educational attainment on RLRS is more negative among black than white respondents (blacks: `r tidy_fert_edu_phen$black$estimate`, 95% C.I. `r tidy_fert_edu_phen$black$conf.low` to `r tidy_fert_edu_phen$black$conf.high`, whites: `r tidy_fert_edu_phen$white$estimate`, 95% C.I. `r tidy_fert_edu_phen$white$conf.low` to `r tidy_fert_edu_phen$white$conf.high`; cf. @goldscheider1969minority, @johnson1979minority, @yang2003big, @maralani2013demography). And the slope of PGS education coefficients on fertility coefficients is larger among black respondents, though imprecisely estimated. But comparisons of PGS selection coefficients between the ethnic groups are hard because of the smaller sample size and differences in the scores' predictive power, so this hypothesis can only be speculative. Another possibility is that the US cohort was exposed to a smaller welfare state than the UK cohort, since many of them had children before the "Great Society" programs of the 1960s.
